\section*{Experience} % (fold)
\label{sec:exp}

\subsection*{2019-23 Substructure lead, Crux project, Shell \textsc{au}} % (fold)
\label{sub:c1}

Responsible for successfully delivering and assuring detailed design. Managed risks, and opportunities concerning installation engineering.

Responsible for successfully delivering the \textsc{define} phase design of the Crux fixed platform structure, which is the deepest among the fixed platforms in the Australian Northwest Shelf.

Improving scope definition with design improvements and savings during \textsc{covid-19}-induced project-freeze period.

Stand-in technical authority for Prelude \textsc{flng} in its operate phase, floater integrity management, steer development and refinement of operate phase performance standards.

% subsection c1 (end)

\subsection*{2015-18 Principal technical expert, Shell \textsc{in}} % (fold)
\label{sub:c2}

Manage, troubleshoot and assist offshore assets in this last-line of defence Shell-wide global functional role. Custodian of the standard for fixed steel offshore structures, recommendations for improvements; support and improve discipline capability.

Marine support + technical assurance to \textsc{bsp} \textsc{calm} buoy replacement project, Bukom \textsc{calm} buoy mooring, and \textsc{blng} jetty rectification project.

Responsible for the development of Crux substructure and topside structure in concept \textsc{select}, and inputs to the Basis for Design.

% subsection c2 (end)

\subsection*{2011--15 Team lead offshore structures, Shell \textsc{my}} % (fold)
\label{sub:c3}

% Support in providing technical grounding, challenge and validation of provisions, fitness of purpose check, and recommendations for standards improvements.

Provide solutions to asset-critical problems concerning safety and performance, e.g., to problems concerning foundations, shallow gas, conductor repair, corrosion, rig-stability, and various other local integrity issues.

Contractor quality audits, structural steel qualification, technical support \& assurance to greenfield, brownfield, drilling, and maintenance projects. %, e.g., modifications, upgrades, and decommissioning.

% Responsible for discipline delivery, accountable for deliverables in concept development and maturation through phases of opportunity, validation and assurance in each phase.

Coach a team of engineers to enable quality discipline delivery, and overall improve team competence.

% subsection c3 (end)

\subsection*{2006--11 Senior engineer, Shell \textsc{nl}} % (fold)
\label{sub:c4}

Responsible for developing seakeeping solutions in intermediate and deepwater \textsc{flng} and \textsc{flso} applications, turret optimization for competitive advantage, development of deep taut mooring rope qualification philosophy.

Responsible for concept development and maturation of gravity based structures, island-type structures, and steel structures.

Responsible for quantitative assessments and review of proposed deviations, technical queries, asset integrity concerns, jackup accidental impacts (Pearl \textsc{gtl}), etc.

% subsection c4 (end)

\subsection*{2000--6 Structural Lead, Technip \textsc{my}} % (fold)
\label{sub:c5}

Accountable for structural deliverables in detailed design projects, viz., design basis, specifications, design reports + drawings, interface with clients and vendors, and conflict resolution arising out of standards, technical ambiguities, specifications, or in practices.

Fabrication support, welding, \textsc{ndt}, testing and review of installation aids. Standby for installation support and troubleshooting.

% subsection c5 (end)

% section exp (end)